### 2020-03-17 thesis/content/chapter-graph-lta.tex
added the lta formulation for the wl_st kernel

In \cref{sec:related:gcr:embed,sec:related:gcr:kernel} three different ways to map a given graph $G$ to a vector $\varphi(G) \in \mathbb{R}^d$ were described:
\begin{enumerate*}
	\item Fingerprint embeddings,
	\item skip-gram inspired embeddings and
	\item kernel embeddings
\end{enumerate*}.
One common way to solve the \ac{gcr} problem via those embedding vectors is to train an \ac{svm} on them.
We will now see that \acp{svm} can be interpreted as \ac{lta} models if they are trained on so-called \acp*{sce}.
\begin{defn}
	Given a a multiset $A = \ldblbrace \underbrace{a_1, \dots, a_1}_{\gamma_A(a_1)\text{ times}},\allowbreak \dots, \underbrace{a_n, \dots, a_n}_{\gamma_A(a_n)\text{ times}} \rdblbrace \subseteq D$, the so-called \textit{multiplicity function} $\gamma_A: D \to \mathbb{N}_0$ maps each element of the domain $D$ to its multiplicity in $A$ with $\gamma_A(x) = 0 \Leftrightarrow x \notin A$.
\end{defn}
\begin{defn}\label{defn:ltag:substruct-embedding}
	A graph embedding $\varphi: \mathcal{G} \to \mathbb{N}_0^{d}$ is called a \ac{sce} iff.\ %
	there are decomposition functions $\psi_{\varphi, i}: \mathcal{G} \to \mathcal{P}(\mathcal{G})$ and functions $\gamma_{\varphi, i}: \mathcal{G} \to (\mathcal{G} \to \mathbb{N}_0)$ for all embedding components $i \in [d]$ s.t.\ %
	$\forall G \in \mathcal{G}, i \in [d]: \varphi(G)[i] = \sum_{c \in \psi_{\varphi, i}(G)} \gamma_{\varphi, i}(G)(c)$ where $\gamma_{\varphi, i}(G): \mathcal{G} \to \mathbb{N}_0$ is the multiplicity function of a multiset of the constituents $\psi_{\varphi, i}(G)$.
	We call $\psi_{\varphi, i}$ an \textit{underlying decomposition} of the $i$-th component of the embedding $\varphi$.
	Similarly the joint decomposition $\psi_{\varphi}(G) \coloneqq \bigcup_{i=1}^d \psi_{\varphi,i}(G)$ is an \textit{underlying decomposition} of $\varphi$.
\end{defn}
Intuitively \cref{defn:ltag:substruct-embedding} states that the value of each \ac{sce} component must be derived from the number of constituents produced by some decomposition function where each constituent might be counted multiple times.
Based on this requirement we now proof the main theorem which shows the relation between \acp{svm} and \ac{lta}.

\begin{thm}\label{thm:ltag:svm-ltag-formulation}
	A binary \ac{svm} graph classifier $h$ that applies a \ac{sce} $\varphi$ to its inputs has an \ac{lta} formulation that uses the underlying decomposition function $\psi_{\varphi}$.
\end{thm}
\begin{proof}
	Let $h: \mathcal{G} \to {\{ -1, +1 \}}$ be a binary graph classifier expressed as $h = h_{\text{\acs*{svm}}} \circ \varphi$ where $\varphi: \mathcal{G} \to \mathbb{N}_0^{d}$ is an \ac{sce} and $h_{\text{\acs*{svm}}}: \mathbb{R}^{d} \to {\{ -1, +1 \}}$ a standard \ac{svm} classifier.
	Additionally, let $\psi_{\varphi}$ be some underlying decomposition of $\varphi$ with ${\{ \gamma_{\varphi, i} \}}_{i=1}^d$ being the corresponding multiplicity functions.

	Based on this decomposition we now bring the \ac{svm} graph classifier $h$ into an \ac{lta} formulation.
	If $h$ is trained on a dataset $\mathcal{D}_{\text{train}} = {\{ (G_1, y_1), \dots, (G_N, y_N) \}}$, via the kernel trick it can be expressed as
	\begin{align*}
		h(G) &= \sgn\left( \sum_{j = 1}^{N} \alpha_j y_j {\langle \varphi(G), \varphi(G_j) \rangle} + b \right)
		\quad\text{for some $\alpha \in \mathbb{R}_{\geq 0}^N$ and $b \in \mathbb{R}$} \\
		&= \sgn\left( {\sum_{i=1}^{d} {
				\varphi(G)[i]
				\underbrace{\left( \sum_{j = 1}^{N} \alpha_j y_j {\varphi(G_j)}[i] \right)}_{\beta_i}}
			} + b \right)
		 = \sgn\left( {\sum_{i=1}^{d} \varphi(G)[i] \beta_i} + b \right) \\
		&= \sgn\left( {\sum_{c_t \in \psi_{\varphi}(G)} \underbrace{\sum_{i = 1}^d \gamma_{\varphi, i}(G)(c_t) \beta_i}_{z_t}} + b \right)
		 = \sgn\left( {\sum_{c_t \in \psi_{\varphi}(G)}} \underbrace{|z_t|}_{w_t} \underbrace{\sgn{z_t}}_{y_t} + {\underbrace{|b|}_{w_b} \underbrace{\sgn{b}}_{y_b}} \right) \\
		&= \wmaj\left( \ldblbrace (y_t, w_t)\, |\, c_t \in \psi_{\varphi}(G) \rdblbrace \cup \ldblbrace (y_b, w_b) \rdblbrace \right)
		\text{.}
	\end{align*}
	By choosing $f_h(c_t) \coloneqq (y_t, w_t)$ and $\mathcal{A}_h(S) = \wmaj(S \cup \ldblbrace (y_b, w_b) \rdblbrace)$, the \ac{svm} model therefore has an \ac{lta} formulation with the decomposition function $\psi_{\varphi}$.
	To see why $\mathcal{A}_h$ satisfies \cref{defn:ltag:weighted-agg}, note that it inherits the idempotency property from $\wmaj$ because $\mathcal{A}_h$ ignores the bias ``pseudo-constituent'' $(y_b, w_b)$ for all threshold weights $\max w_t \geq \eta > w_b$, similarly the zero invariance of $\wmaj$ is also directly inherited.
	This concludes the proof.
\end{proof}

The central statement of \cref{thm:ltag:svm-ltag-formulation} is that \acs{svm} graph classifiers that use an \ac{sce} $\varphi$ implicitly perform an \acs{lta}-like weighted majority vote aggregation of constituent scores $y_t$.
Those constituent scores can in turn be expressed as a majority vote of the graph scores in the training dataset $\mathcal{D}_{\text{train}}$:
\begin{align}
	y_t \coloneqq \sgn z_t
	 &= \sgn\left( \sum_{j=1}^N \underbrace{\left( \alpha_j \smashoperator[l]{\sum_{c_k \in \psi_{\varphi}(G_j)}} \sum_{i=1}^d \gamma_{\varphi,i}(G)(c_t) \gamma_{\varphi,i}(G_j)(c_k) \right)}_{w_j} y_j \right) \\
	 &= \wmaj(\ldblbrace (y_j, w_j)\, |\, j \in [N] \rdblbrace) \nonumber
\end{align}
Note that, if the constituents of $G_j$ all come from different embedding components than those of $G$ ($\forall i \in [d]: {\psi_{\varphi, i}(G_j) \cap \psi_{\varphi, i}(G)} = \emptyset$), then $G_j$ has no influence on the score of $G$ ($w_j = 0$).

To see what \cref{thm:ltag:svm-ltag-formulation} implies in practice, we will now apply it to the graph embedding approaches described in \cref{sec:related:gcr:embed,sec:related:gcr:kernel}:
\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Fingerprint embeddings:}
		Here the $i$-th embedding component represent the number of occurrences of a substructure $S_i$, i.e.\ ${\varphi}_{\text{FP}}(G)[i] \coloneqq \mathit{count}_{S_i}(G)$ (see \cfullref{defn:related:wl-count-detect}).
		Such a fingerprint embedding naturally is an \ac{sce} with the decomposition functions $\psi_{\text{FP}, i}(G) \coloneqq \{ G[\set(s)]\, |\, s \in \mathcal{V}_G^{*} \land G[s] \equiv S_i \}$ and the multiplicity functions $\gamma_{\text{FP}, i}(G)(c) \coloneqq \mathbbm{1}[c \in \psi_{\text{FP}, i}(G)]$. % chktex 21

		Under the assumption that the substructure patterns $S_i$ are chosen s.t.\ the their instances $c \in \psi_{\text{FP}, i}(G)$ are nontrivial interpretable constituents, the underlying joint decomposition $\psi_{\text{FP}}(G) \coloneqq \bigcup_{i=1}^d \psi_{\text{FP}, i}(G)$ must also be nontrivial and interpretable.
		Thus, by \cref{thm:ltag:svm-ltag-formulation}, \acp{svm} trained on fingerprint embeddings are \ac{lta} models that produce locally explainable predictions.
		\badgebox[t_green]{\cmark\ LTA}
	\item \textbf{\texttt{graph2vec}:}
		The skip-gram inspired \texttt{graph2vec} embedding produces vectors $\text{FP}(G) \in \mathbb{R}^d$ whose individual components do not have a clear interpretation.
		Since the component values can be arbitrary reals, this approach is not an \ac{sce} which in turn implies that it does not have an \ac{lta} formulation as in \cref{thm:ltag:svm-ltag-formulation}.
		\badgebox[t_red]{\xmark\ non-LTA}
	\item \textbf{\ac{wl} subtree kernel:}
		The individual components of the \ac{wl} subtree embedding represent the number of occurrences of a color $c_i \in \mathcal{C}$, i.e.\ $\varphi_{\text{ST}}(G)[i] \coloneqq \mathit{dist}_{\chi_{G,1}^{(t)}}(c_i)$ as defined in \cfullref[ on ]{eq:related:wl-subtree-kernel}.
		As illustrated in \cfullref[ on ]{fig:related:wl-subtree}, each occurrence of a color $c_i$ in the \ac{wl} coloring $\chi_{G,1}^{(t)}$ corresponds to the occurrence of a breadth-first subtree of depth $t$.
		\badgebox[t_green]{\cmark\ LTA-like}
	\item \textbf{\ac{wl} shortest path kernel:}
		\badgebox[t_red]{\xmark\ non-LTA}
	\item \textbf{$k$-LWL kernel:}
		\badgebox[t_green]{\cmark\ LTA-like}
	\item \textbf{$k$-GWL kernel:}
		\badgebox[t_red]{\xmark\ non-LTA}
\end{enumerate}

>>>>

In \cref{sec:related:gcr:embed,sec:related:gcr:kernel} three different ways to map a given graph $G$ to a vector $\varphi(G) \in \mathbb{R}^d$ were described:
\begin{enumerate*}
	\item Fingerprint embeddings,
	\item skip-gram inspired embeddings and
	\item kernel embeddings
\end{enumerate*}.
One common way to solve the \ac{gcr} problem via those embedding vectors is to train an \ac{svm} on them.
We will now see that \acp{svm} can be interpreted as \ac{lta} models if they are trained on so-called \acp*{sce}.
\begin{defn}
	Given a a multiset $A = \ldblbrace \underbrace{a_1, \dots, a_1}_{\gamma_A(a_1)\text{ times}},\allowbreak \dots, \underbrace{a_n, \dots, a_n}_{\gamma_A(a_n)\text{ times}} \rdblbrace \subseteq D$, the so-called \textit{multiplicity function} $\gamma_A: D \to \mathbb{N}_0$ maps each element of the domain $D$ to its multiplicity in $A$ with $\gamma_A(x) = 0 \Leftrightarrow x \notin A$.
\end{defn}
\begin{defn}\label{defn:ltag:substruct-embedding}
	A graph embedding $\varphi: \mathcal{G} \to \mathbb{N}_0^{d}$ is called a \ac{sce} iff.\ %
	there are decomposition functions $\psi_{\varphi, i}: \mathcal{G} \to \mathcal{P}(\mathcal{G})$ and multiplicity functions $\gamma_{\varphi, i}: \mathcal{G} \to \mathbb{N}_0$ for all embedding components $i \in [d]$ s.t.\ %
	$\forall G \in \mathcal{G}, i \in [d]: \varphi(G)[i] = \sum_{c \in \psi_{\varphi, i}(G)} \gamma_{\varphi, i}(c)$ where $\gamma_{\varphi, i}$ is the multiplicity function of a multiset of the constituents $\psi_{\varphi, i}(G)$.
	We call $\psi_{\varphi, i}$ an \textit{underlying decomposition} of the $i$-th component of the embedding $\varphi$.
	Similarly the joint decomposition $\psi_{\varphi}(G) \coloneqq \bigcup_{i=1}^d \psi_{\varphi,i}(G)$ is an \textit{underlying decomposition} of $\varphi$.
\end{defn}
Intuitively \cref{defn:ltag:substruct-embedding} states that the value of each \ac{sce} component must be derived from the number of constituents produced by some decomposition function where each constituent might be counted multiple times.
Based on this requirement we now proof the main theorem which shows the relation between \acp{svm} and \ac{lta}.

\begin{thm}\label{thm:ltag:svm-ltag-formulation}
	A binary \ac{svm} graph classifier $h$ that applies a \ac{sce} $\varphi$ to its inputs has an \ac{lta} formulation that uses an underlying decomposition $\psi_{\varphi}$ of $\varphi$.
\end{thm}
\begin{proof}
	Let $h: \mathcal{G} \to {\{ -1, +1 \}}$ be a binary graph classifier expressed as $h = h_{\text{\acs*{svm}}} \circ \varphi$ where $\varphi: \mathcal{G} \to \mathbb{N}_0^{d}$ is an \ac{sce} and $h_{\text{\acs*{svm}}}: \mathbb{R}^{d} \to {\{ -1, +1 \}}$ a standard \ac{svm} classifier.
	Additionally, let $\psi_{\varphi}$ be some underlying decomposition of $\varphi$ with ${\{ \gamma_{\varphi, i} \}}_{i=1}^d$ being the corresponding multiplicity functions.

	Based on this decomposition we now bring the \ac{svm} graph classifier $h$ into an \ac{lta} formulation.
	If $h$ is trained on a dataset $\mathcal{D}_{\text{train}} = {\{ (G_1, y_1), \dots, (G_N, y_N) \}}$, via the kernel trick it can be expressed as
	\begin{align*}
		h(G) &= \sgn\left( \sum_{j = 1}^{N} \alpha_j y_j {\langle \varphi(G), \varphi(G_j) \rangle} + b \right)
		\quad\text{for some $\alpha \in \mathbb{R}_{\geq 0}^N$ and $b \in \mathbb{R}$} \\
		&= \sgn\left( {\sum_{i=1}^{d} {
				\varphi(G)[i]
				\underbrace{\left( \sum_{j = 1}^{N} \alpha_j y_j {\varphi(G_j)}[i] \right)}_{\beta_i}}
			} + b \right)
		 = \sgn\left( {\sum_{i=1}^{d} \varphi(G)[i] \beta_i} + b \right) \\
		&= \sgn\left( {\sum_{c_t \in \psi_{\varphi}(G)} \underbrace{\sum_{i = 1}^d \gamma_{\varphi, i}(c_t) \beta_i}_{z_t}} + b \right)
		 = \sgn\left( {\sum_{c_t \in \psi_{\varphi}(G)}} \underbrace{|z_t|}_{w_t} \underbrace{\sgn{z_t}}_{y_t} + {\underbrace{|b|}_{w_b} \underbrace{\sgn{b}}_{y_b}} \right) \\
		&= \wmaj\left( \ldblbrace (y_t, w_t)\, |\, c_t \in \psi_{\varphi}(G) \rdblbrace \cup \ldblbrace (y_b, w_b) \rdblbrace \right)
		\text{.}
	\end{align*}
	By choosing $f_h(c_t) \coloneqq (y_t, w_t)$ and $\mathcal{A}_h(S) = \wmaj(S \cup \ldblbrace (y_b, w_b) \rdblbrace)$, the \ac{svm} model therefore has an \ac{lta} formulation with the decomposition function $\psi_{\varphi}$.

	To complete the proof it now remains to show that $f_h$ and $\mathcal{A}_h$ are in fact a local evaluation function and a weighted aggregation function respectively.
	To see that $f_h$ perform local evaluation, note that $f_h(c_t) \coloneqq (\sgn z_t, {|z_t|})$ with $z_t \coloneqq \sum_{i=1}^{d} \gamma_{\varphi,i}(c_t) \beta_i$ only depends on the shared multiplicity functions $\gamma_{\varphi,i}$, the constants $\beta_i$ and the constituent $c_t$;
	apart from $c_t$ no other information from the input graph $G$ is required by $f_h$ which makes it a local evaluation function.
	To see why $\mathcal{A}_h$ satisfies \cref{defn:ltag:weighted-agg}, note that it inherits the idempotency property from $\wmaj$ because $\mathcal{A}_h$ ignores the bias ``pseudo-constituent'' $(y_b, w_b)$ for all threshold weights $\max w_t \geq \eta > w_b$, similarly the zero invariance of $\wmaj$ is also directly inherited.
	This concludes the proof.
\end{proof}

The central statement of \cref{thm:ltag:svm-ltag-formulation} is that \acs{svm} graph classifiers that use an \ac{sce} $\varphi$ implicitly perform an \acs{lta}-like weighted majority vote aggregation of constituent scores $y_t$.
Those constituent scores can in turn be expressed as a majority vote of the graph scores in the training dataset $\mathcal{D}_{\text{train}}$:
\begin{align}
	y_t \coloneqq \sgn z_t
	 &= \sgn\left( \sum_{j=1}^N \underbrace{\left( \alpha_j \smashoperator[l]{\sum_{c_k \in \psi_{\varphi}(G_j)}} \sum_{i=1}^d \gamma_{\varphi,i}(c_t) \gamma_{\varphi,i}(c_k) \right)}_{w_j} y_j \right) \\
	 &= \wmaj(\ldblbrace (y_j, w_j)\, |\, j \in [N] \rdblbrace) \nonumber
\end{align}
Note that, if the constituents of $G_j$ all come from different embedding components than those of $G$ ($\forall i \in [d]: {\psi_{\varphi, i}(G_j) \cap \psi_{\varphi, i}(G)} = \emptyset$), then $G_j$ has no influence on the score of $G$ ($w_j = 0$).

To see what \cref{thm:ltag:svm-ltag-formulation} implies in practice, we will now apply it to the graph embedding approaches described in \cref{sec:related:gcr:embed,sec:related:gcr:kernel}:
\begin{enumerate}[label=\textbf{\arabic*.}]
	\item \textbf{Fingerprint embeddings:}
		Here the $i$-th embedding component represent the number of occurrences of a substructure $S_i$, i.e.\ ${\varphi}_{\text{FP}}(G)[i] \coloneqq \mathit{count}_{S_i}(G)$ (see \cfullref{defn:related:wl-count-detect}).
		Such a fingerprint embedding naturally is an \ac{sce} with the decomposition functions $\psi_{\text{FP}, i}(G) \coloneqq \{ G[\set(s)]\, |\, s \in \mathcal{V}_G^{*} \land G[s] \equiv S_i \}$ and the multiplicity functions $\gamma_{\text{FP}, i}(c) \coloneqq \mathbbm{1}[c \simeq S_i]$ since those functions produce the subgraphs that are counted by ${\varphi}_{\text{FP}}(G)[i]$ with multiplicity $1$. % chktex 21

		Under the assumption that the substructure patterns $S_i$ are chosen s.t.\ the their instances $c \in \psi_{\text{FP}, i}(G)$ are nontrivial interpretable constituents, the underlying joint decomposition $\psi_{\text{FP}}(G) \coloneqq \bigcup_{i=1}^d \psi_{\text{FP}, i}(G)$ must also be nontrivial and interpretable.
		Thus, by \cref{thm:ltag:svm-ltag-formulation}, \acp{svm} trained on fingerprint embeddings are \ac{lta} models that produce locally explainable predictions.
		\badgebox[t_green]{LTA}
	\item \textbf{\texttt{graph2vec}:}
		The skip-gram inspired \texttt{graph2vec} embedding produces vectors $\varphi(G) \in \mathbb{R}^d$ whose individual components do not have a clear interpretation.
		\texttt{graph2vec} embeds graphs that have common 1-\acs{wl} colors closer to each other than graphs that do not share the same colors (see \cfullref{eq:related:graph2vec}).
		The resulting component values can be arbitrary reals, therefore this approach is not an \ac{sce} which in turn implies that it does not have an \ac{lta} formulation as in \cref{thm:ltag:svm-ltag-formulation}.
		\badgebox[t_red]{non-LTA}
	\item \textbf{\ac{wl} subtree kernel:}
		The individual components of the \ac{wl} subtree kernel's embedding $\varphi_{\text{ST}}$ represent the number of occurrences of a color $\kappa_i \in \mathcal{C}$, i.e.\ $\varphi_{\text{ST}}(G)[i, t] \coloneqq \mathit{dist}_{\chi_{G,1}^{(t)}}(\kappa_i)$ as defined in \cfullref[ on ]{eq:related:wl-subtree-kernel}\footnote{
			To avoid confusion $\kappa_i \in \mathcal{C}$ is used for colors and $c_j \in \mathcal{G}$ for constituents in this context.
		}.
		The occurrence of a color $\kappa_i$ at some vertex $v_j \in \mathcal{V}_G$ in the $t$-th refinement step (i.e.\ $\chi_{G,1}^{(t)}(v_j) = \kappa_i$) in turn implies that the \ac{bfs} tree $S_{j,t} \coloneqq \text{\acs*{bfs}}(G, v_j, t)$ of depth $t$ rooted at $v_j$ is isomorphic to some \ac{wl} color subtree $S_{\kappa_i}$ (i.e.\ $S_{j,t} \simeq S_{\kappa_i}$).
		This relation between \ac{wl} colors $\kappa_i$ and subtrees $S_{\kappa_i}$ was illustrated in \cfullref[ on ]{fig:related:wl-subtree}.

		To show that $\varphi_{\text{ST}}$ is an \ac{sce}, we have to define decomposition functions $\psi_{\varphi, i, t}$ and multiplicity functions $\gamma_{\varphi, i, t}$ s.t.\ $\varphi(G)[i, t] = \sum_{c \in \psi_{\varphi, i, t}(G)} \gamma_{\varphi, i, t}(c)$.
		Since $\varphi(G)[i, t]$ counts the occurrences $S_{j,t}$ of a subtree $S_{\kappa_i}$ in $G$, the \ac{sce} requirement would be trivially satisfied if each $S_{j,t}$ were a constituent with multiplicity $1$.
		This intuition is however not quite correct because the constituents of a graph $G$ must be induced subgraphs of $G$, not \ac{bfs} subtrees $S_{j, t}$ of $G$.
		\begin{figure}[t]
			\centering
			\includegraphics[width=\linewidth]{gfx/graph-lta/wl1-constituents.pdf}
			\caption[The constituents implied by the \ac{wl} subtree kernel embedding for an example graph.]{
				The constituents $c_{j,t}$ implied by the \ac{wl} subtree embedding vector $\varphi(G) = (\underbrace{\textcolor{t_blue}{4}, \textcolor{t_red}{0}, \textcolor{t_green}{0}, \textcolor{t_darkyellow}{0}}_{t = 0}, \underbrace{\textcolor{t_blue}{0}, \textcolor{t_red}{2}, \textcolor{t_green}{1}, \textcolor{t_darkyellow}{1}}_{t = 1})$. % chktex 25
				The subtrees $S_{j,t}$ that span each constituent $c_{j,t}$ are visualized by the colored arrows that originate from the colored root vertices.
				Because $S_{1,1}$ and $S_{2,1}$ span the same constituent $c = c_{1,1} = c_{2,1} = G[\{ v_1, v_2, v_3 \}]$, its multiplicity is $\gamma_{\varphi, \textcolor{t_red}{\texttt{B}}, 1}(c) = 2$; % chktex 25
				the multiplicity of all other constituents is $1$.
			}\label{fig:ltag:wl1-constituents}
		\end{figure}

		To fix the previous intuition we ``convert'' the subtrees $S_{j, t}$ into proper subgraph constituents via $c_{j,t} \coloneqq G[\mathcal{V}_{S_{j,t}}]$, i.e.\ the subgraphs that are spanned by the subtrees.
		The resulting decomposition functions are $\psi_{\varphi, i, t}(G) \coloneqq \{ c_{j,t}\, |\, {v_j \in \mathcal{V}_G}\,\land {S_{j,t} \simeq S_{\kappa_i}} \}$. % chktex 21
		As illustrated in \cref{fig:ltag:wl1-constituents}, the number of distinct constituents $c_{j,t}$ might be smaller than the number of \ac{bfs} subtrees $S_{j,t}$ because two distinct subtrees might span the same set of vertices.
		To fix this discrepancy between the subtree occurrence count (which equals $\varphi(G)[i, t]$) and the number of constituents, the multiplicities $\gamma_{\varphi, i, t}(c)$ of the constituents $c$ have to correspond to the number of \ac{bfs} subtrees they were spanned up by, i.e.\
		\begin{align*}
			\gamma_{\varphi, i, t}(c) &\coloneqq {|\{ S = \text{\acs*{bfs}}(c, v_{\text{root}}, t)\, |\, v_{\text{root}} \in \mathcal{V}_c \land S \simeq S_{\kappa_i} \land \mathit{complete}(S) \}|} \\
			\text{with }\mathit{complete}(S) &\Leftrightarrow \forall\ \text{leaf nodes $v_{\text{leaf}}$ of the tree $S$}: {|\Gamma_c(v_{\text{leaf}})|} = {|\Gamma_G(v_{\text{leaf}})|}
			\text{.}
		\end{align*}
		The purpose of the $\mathit{complete}(S)$ condition is to only count the \ac{bfs} subtrees of the constituent $c$ that are also \ac{bfs} subtrees of the complete graph $G$.
		To see why this is required, note that in \cref{fig:ltag:wl1-constituents} the $c_{1,1}$/$c_{2,1}$ constituent contains the color subtree $S_{\textcolor{t_red}{\texttt{B}}}$ three times (rooted at $v_1$, $v_2$ and $v_3$) even though $G$ only contains it twice (rooted at $v_1$ and $v_2$). % chktex 25
		Also note that, since $\gamma_{\varphi, i, t}(c)$ must only depend on a given constituent $c$ and not on the graph $G$ it was decomposed from, the degree information $|\Gamma_G(v_{\text{leaf}})|$ of the constituent vertices $v \in \mathcal{V}_c$ is assumed to be statically encoded in the labels $l_c[v]$ or feature vectors $x_c[v]$.

		Via the decomposition and multiplicity functions that were just described, $\varphi_{\text{ST}}$ is in fact an \ac{sce} with a nontrivial, subtree-based decomposition function.
		By \cref{thm:ltag:svm-ltag-formulation} \acp{svm} that use the \ac{wl} subtree kernel therefore have nontrivial \ac{lta} formulations, i.e.\ they can be considered to be ``\ac{lta}-like'' models.
		However, unlike fingerprint embeddings, the \ac{wl} subtree constituents are not manually chosen to be interpretable.
		This implies that the localized explainability characteristic of \ac{lta} is only partially satisfied since the \ac{svm} predictions are based on local constituent predictions that are not necessarily interpretable.
		\badgebox[t_green]{LTA-like}
	\item \textbf{\ac{wl} shortest path kernel:}
		\badgebox[t_red]{non-LTA}
	\item \textbf{$k$-LWL kernel:}
		\badgebox[t_green]{LTA-like}
	\item \textbf{$k$-GWL kernel:}
		\badgebox[t_red]{non-LTA}
\end{enumerate}
